Model Samples Processing

### 2020-02-13 stats/model_sample_processing.Rmd
peek at chain 5 fb model

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

>>>>

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)%>%
mutate(model = "fullBayes")
